### 2012-08-27 docs/paper.tex
added latex file

%\documentclass[4pt,a4paper]{article}
\documentclass[4pt,a4paper,twocolumn]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{algorithm}
\usepackage{textcomp}
\usepackage{fontenc}
\usepackage{tipa}
\usepackage{framed}
\usepackage{multicol}
\usepackage{color}
\usepackage{qtree}
\usepackage{graphicx}
\usepackage{amsmath}

\author{David Przybilla\footnote{dav.alejandro@gmail.com , davida@coli.uni-saarland.de}\\ Term Paper for Unsupervised Semisupervised
Learning Seminar\\ Saarland University}
\title{Short Text Topic Classification using Label Propagation}
\begin{document}
\twocolumn[
	 \begin{@twocolumnfalse}
    \maketitle
    \begin{abstract}
      ...
    \end{abstract}
  \end{@twocolumnfalse}
  ]

\part*{Introduction}
Twitter and Tuenti are popular microblogging services in Latinamerica,
as prices of Smartphones became more accessible to people big communities
have grown around this services.\\
These communities are actively commenting everything from political events to products experiences.\\
Therefore it has become of interest for many companies to analyze the microblogging data in order to understand
what their clients want of their products, this led naturally to sentiment Analysis.\\ 
\\
One of the subtasks of Sentiment Analysis is to find the Topic or Aspect of an opinion,
for example given a set of opinions about a mobile phone, it is possible to label each comment
with the topic that it is referring to, this labels could be ``battery", ``design", ``operative system" etc.
This Subtask can be modelled as a classification problem, given a set of fixed possible topics.\\
\\
In this paper a semisupervised technique is used in order to label the topic of a set of comments 
related to a product or service.\\
The semi supervised techniques presents two advantages.\\
First by using semisupervised methods the amount of neccessary annotateed data is less,
and second the unlabeled data is used during training, this is important since the amount of unlabeled data in these tasks is abundant and available.\\
\\

Though Classifying text has been a widely studied topic,the focus has been on long documents,
whereas tweets are at most 144 characters long.\\
The new trends in these social networks have led to research about classification in short texts, the latter has  shown that it arises new challenges, and previous approaches are not  effective.\\
One of the reasons is that  user generated comments in the mentioned services tend to be extremly short, leading to sparce feature representations.\\
\\
In respect to short text classification X proposes [xxxxreferencesherexxxx] to do Feature Extension to deal with data sparcity, in his approach each comment is extended with extra words from an expansion vocabulary.
[Overcoming the Brittleness Bottleneck using Wikipedia:
Enhancing Text Categorization with Encyclopedic Knowledge] proposes on the other hand to use enciclopedic knowledge from wikipedia for extending the short commetns.
As opposed to [Short Text Classification Using Very Few Words] who reduces even more the word space of the comments by using information retrieval voting schemes.\\
\\
In this paper, a Semisupervised technique called Label propagation is used
in order to label a set of tweets about product reviews.\\
Label propagation is reviewed in part X.\\
Since data sparcity showed to be a problem a way for handling it
is discuss in in part Y using an approach Z.\\
The results are given in the part W.

\part*{Pre-processing}

Since the datasets used in this experiment are real data crawled from twitter and other sources there is a lot of noise in them.\\
Some of the problems are (but not limited) to:\\
\begin{itemize}
	\item Miss spelled words, from typo errors to lack of accents.
	\item Internet Language, replacing some letters for others whose phonetics are similar i.e: ``\textbf{qu}iero" (I want) for ``\textbf{k}iero", abbreviations and expressions (``Jaja'' ``jiji" ... )
	\item Twitter Jargon such as: ``RT:",``@", hashtags and mentions. 
\end{itemize}

The preprocessing done was the following:
\begin{enumerate}
	\item Remove Strange characters, such as hearts, and other unicode characters
	\item Remove some of the Twitter Jargon 
	\item Use TreeTagger [ http://www.ims.uni-stuttgart.de/projekte/corplex/TreeTagger/]for getting the part of speech and the stem of each word in each comment
	\item discard those words that are not adjectives, nouns or verbs
	\item replace each word by its stem in lowercase
	\item remove accents from words
\end{enumerate}

\part*{Label Propagation}

\part*{Feature Generation}
\part*{Structure Learning}

\part*{Experiment}
Meridean [reference to meridean] is a Colombian company which extracts and saves tweets
mentioning latinamerican companies or products.\\
Basically they mine  tweets and offer sentiment analysis services to companies.\\
The range of products reviews go from Electronic Devices to Sanitary Products.\\
\\
The experiment use two of their Collections of product reviews.\\
The first DataSet review a mobilephone, the second dataset review a Sanitary product.\\
\\
La

\part*{Results}
\part*{Future Work}

\end{document}

### 2012-08-27 docs/paper.tex
fixed bib

@@
 \usepackage{amsmath}
+\usepackage{hyperref}
+
+\hypersetup{  
+    linkcolor=red,          % color of internal links
+    citecolor=green,        % color of links to bibliography
+    filecolor=magenta,      % color of file links
+    urlcolor=cyan           % color of external links
+}
 
@@
 is discuss in in part Y using an approach Z.\\
-The results are given in the part W.
+The results are given in the part W.\\
+The source code of the implementation is available at \url{https://github.com/dav009/LPForTopicIdentification},the datasets however are not public, since they are constrained by a permission license.
 
@@
 	\item Remove some of the Twitter Jargon 
-	\item Use TreeTagger [ http://www.ims.uni-stuttgart.de/projekte/corplex/TreeTagger/]for getting the part of speech and the stem of each word in each comment
+	\item Use TreeTagger \href{http://www.ims.uni-stuttgart.de/projekte/corplex/TreeTagger/}{TreeTagger} \ref{Schmid94probabilisticpart-of-speech} for getting the part of speech and the stem of each word in each comment
 	\item discard those words that are not adjectives, nouns or verbs
@@
 \part*{Results}
+
 \part*{Future Work}
 
+\bibliography{paper}
+
 \end{document}

### 2012-08-27 main.py

@@ -16,6 +16,7 @@ from  Queue import PriorityQueue
 from utils.wordPredictor import wordPredictor
 from utils.wordPredictor import trainPredictors
 from copy import deepcopy
+from utils.frencuencyTable import frecuencyTable
 
 #measures the distance among two vectors, test gitplugin5
 def distance(v1,v2,similarityMeasure):
@@ -43,11 +44,14 @@ def distance(v1,v2,similarityMeasure):
 				return result
 
 def main():
+
+	#table frquencuency of all the words in the messages
+	frecuencies=frecuencyTable()
 	
 	#Read the file and convert triples into objects
 	
 	#read file with messages
-	listOfTriples=readCSV("Data/sony.csv")
+	listOfTriples=readCSV("Data/sonyReduced.csv")
 	
 	listOfData=[]
 	#convert the triples to objects
@@ -74,6 +78,15 @@ def main():
 		for v in currentVocabulary:
 			setOfWords.add(v)
 
+		for word in instance.triple['message'].split(" "):
+			frecuencies.add(word)
+
+	listOfWordsByValue=frecuencies.sort_by_value()
+	print "words by frequencie---"
+	for wordd in listOfWordsByValue:
+		print wordd
+	print "--------------------------"
+
 	print "looking for PMI"
 	#get the instances which are annotated
 	listOfAnnotatedData=[]
@@ -96,7 +109,7 @@ def main():
 		while not queue.empty() and currentCount<numberOfDimensions:
 			pmi=queue.get()[1]
 			
-			if(pmi['pmi']>-2): #not taking into account the pmi
+			if(pmi['pmi']>0.3): #not taking into account the pmi
 				print pmi['word']+"--"+str(pmi['pmi'])+"--"+pmi['label']
 				currentCount=currentCount+1
 				setOfSelectedWords.add(pmi['word'])
@@ -228,17 +241,22 @@ def  justGenerateSeeds(percentage):
 	#seed files refer to those instances which label is already given
 	seedFileContent=""
 	seedFile=open("seeds_"+str(percentage),'w')
+
+	SetOfSeeds=Set()
 	
 	for instance in instanceVectors:
-		if ( (not instance.triple['label']=='') and (not instance.triple['label']==None) ):
+		if ( (not instance.triple['label']=='') and (not instance.triple['label']==None) and not instance.triple['message'] in SetOfSeeds):
[…]

### 2012-08-27 processing/cleaning.py

@@ -8,7 +8,7 @@ import os
 from nltk.corpus import stopwords
 
 #PATH OF TREETRAGGER
-TREE_TAGGER_PATH="stemming/treeTagger/cmd/"
+TREE_TAGGER_PATH="/home/attickid/LPproject/LPForTopicIdentification/processing/stemming/treeTagger/cmd/"
 
 #given a message returns a message steamed
 def stemming(message):

### 2012-08-27 utils/frencuencyTable.py

@@ -33,4 +33,4 @@ class frecuencyTable:
 	    items=self.table.items()
 	    backitems=[ [v[1],v[0]] for v in items]
 	    backitems.sort()
-	    return [ backitems[i][1] for i in range(0,len(backitems))]
+	    return backitems

### 2012-08-28 docs/paper.tex
added bib support

@@
 \usepackage{amsmath}
-\usepackage{hyperref}
 
+\usepackage{cite}
+\usepackage{lastpage}
+\usepackage{lmodern}
+
+\usepackage[]{hyperref}
 \hypersetup{  
-    linkcolor=red,          % color of internal links
-    citecolor=green,        % color of links to bibliography
-    filecolor=magenta,      % color of file links
+	colorlinks=true,
     urlcolor=cyan           % color of external links
@@
 Enhancing Text Categorization with Encyclopedic Knowledge] proposes on the other hand to use enciclopedic knowledge from wikipedia for extending the short commetns.
-As opposed to [Short Text Classification Using Very Few Words] who reduces even more the word space of the comments by using information retrieval voting schemes.\\
+As opposed to ~\cite{Sun:2012:STC:2348283.2348511} who reduces even more the word space of the comments by using information retrieval voting schemes.\\
 \\
@@
 	\item Remove some of the Twitter Jargon 
-	\item Use TreeTagger \href{http://www.ims.uni-stuttgart.de/projekte/corplex/TreeTagger/}{TreeTagger} \ref{Schmid94probabilisticpart-of-speech} for getting the part of speech and the stem of each word in each comment
+	\item Use \href{http://www.ims.uni-stuttgart.de/projekte/corplex/TreeTagger/}{TreeTagger} ~\cite{Schmid94probabilisticpart-of-speech} for getting the part of speech and the stem of each word in each comment
 	\item discard those words that are not adjectives, nouns or verbs
@@
 
-\bibliography{paper}
+\bibliography{paper}{}
+\bibliographystyle{alpha}
 

### 2012-08-28 main.py
Junto graph function separated from main for readability

@@ -18,6 +18,8 @@ from utils.wordPredictor import trainPredictors
 from copy import deepcopy
 from utils.frencuencyTable import frecuencyTable
 
+
+
 #measures the distance among two vectors, test gitplugin5
 def distance(v1,v2,similarityMeasure):
 		result=0.0
@@ -42,6 +44,18 @@ def distance(v1,v2,similarityMeasure):
 				
 				
 				return result
+
+#given a path to a file and a list of vectors it generates a junto graph
+def createJuntoGraph(path,instanceVectors):
+	#creates a file with the graph description for JUNTO to use
+	graphFile=open(path,'w')
+	juntoGraphFileContent=""
+
+	for i in range(0,len(instanceVectors)):
+		for j in range(i+1,len(instanceVectors)):
+			distanceValue=distance(matrixLSA[i],matrixLSA[j],'cosine')
+			juntoGraphFileContent=juntoGraphFileContent+str(i)+"\t"+str(j)+"\t"+str(distanceValue)+"\n"
+	graphFile.write(juntoGraphFileContent)
 
 def main():
 
@@ -159,19 +173,13 @@ def main():
 	print matrixLSA
 
 	print "calculating the graph files for Junto"
-	#measure the similarities
-	similarities={}
-	#creates a file with the graph description for JUNTO to use
-	graphFile=open("input_graph",'w')
-	juntoGraphFileContent=""
+	
 
-	for i in range(0,len(instanceVectors)):
-		for j in range(i+1,len(instanceVectors)):
-			distanceValue=distance(matrixLSA[i],matrixLSA[j],'cosine')
-			similarities[str(i)+'_'+str(j)]=distanceValue
-			
-			juntoGraphFileContent=juntoGraphFileContent+str(i)+"\t"+str(j)+"\t"+str(distanceValue)+"\n"
-	graphFile.write(juntoGraphFileContent)
+
+	#creates a junt graph
+	createJuntoGraph('input_graph',instaceVectors)
+
+
 
 	#this defines the number of seeds(annotated data for the algorithm)
 	percentageOfSeeds=0.1

### 2012-08-28 processing/cleaning.py
Added funciton for removing accents, and removing noise from differnt twitter features

@@ -5,10 +5,27 @@
 #4.get frecuency tables.
 #5.generating JUNTO graph format
 import os
+import unicodedata
+import re
 from nltk.corpus import stopwords
 
 #PATH OF TREETRAGGER
 TREE_TAGGER_PATH="/home/attickid/LPproject/LPForTopicIdentification/processing/stemming/treeTagger/cmd/"
+
+
+#remove accents
+def removeAccents(message):
+	returnMessage=""
+	for word in message.split(" "):
+		returnMessage=returnMessage+" "+removeAccentsFromWord(word).decode('utf-8')
+
+	print "cleaned accents"
+	print returnMessage
+	return returnMessage.strip()
+
+
+def removeAccentsFromWord(word):
+	return unicodedata.normalize('NFKD',word.decode('utf-8')).encode('ASCII', 'ignore').decode()
 
 #given a message returns a message steamed
 def stemming(message):
@@ -36,10 +53,35 @@ def stemming(message):
 
 #given a text returns a version of text where all the stop words are removed (cast the text into lowercase)
 def removeStopWords(message):
+
+	#look for patterns of twitter noise
+	 #pattern for mentions
+	p = re.compile( '@(\w)+')
+	message=p.sub("",message)
+
+	 #pattern for laughs
+	p = re.compile( 'jaja(ja)*')
+	message=p.sub("",message)
+
+	p = re.compile( 'jiji(ji)*')
+	message=p.sub("",message)
+
+	p = re.compile( 'jeje(je)*')
+	message=p.sub("",message)
+
+	p = re.compile( 'haha(ha)*')
+	message=p.sub("",message)
+
+	p = re.compile( 'w(w)*(o)+(w)*w')
+	message=p.sub("",message)
+
+	p = re.compile( '|')
+	message=p.sub("",message)
+
 	newMessage=""
 	
 	
-	forbiddenList=[",",".","!","?","\n","\t","(",")",',',"me","le","jaja","jeje","wow","jiji","haha"]
+	forbiddenList=["|",".","!","?","\n","\t","(",")",',',"me","le","jaja","jeje","wow","jiji","haha","te","yo","rt","rt:"]
 	#replaces the word of forbiddenlsit
 	for word in forbiddenList:
 		message=message.replace(word,'');
@@ -52,8 +94,8 @@ def removeStopWords(message):
 		if ((not word in stopwords.words('spanish')) and not(word==" ")):
[…]

### 2012-08-28 main.py
Added support for creating a svm classifier

@@ -15,6 +15,7 @@ from math import degrees
 from  Queue import PriorityQueue
 from utils.wordPredictor import wordPredictor
 from utils.wordPredictor import trainPredictors
+from utils.wordPredictor import trainSVMPredictoForLabels
 from copy import deepcopy
 from utils.frencuencyTable import frecuencyTable
 
@@ -46,7 +47,7 @@ def distance(v1,v2,similarityMeasure):
 				return result
 
 #given a path to a file and a list of vectors it generates a junto graph
-def createJuntoGraph(path,instanceVectors):
+def createJuntoGraph(path,instanceVectors,matrixLSA):
 	#creates a file with the graph description for JUNTO to use
 	graphFile=open(path,'w')
 	juntoGraphFileContent=""
@@ -80,12 +81,16 @@ def main():
 		print "cleaning: "+str(instance.triple['id'])
 
 		#stores the labels
-		if(instance.triple['label']!=None and instance.triple['label']!=''):
-			setOfLabels.add(instance.triple['label'])
+
 
 		#clean message
 		instance.cleanMessage()
 		instance.measureFrequencies()
+
+		if(instance.triple['label']!=None and instance.triple['label']!=''):
+			setOfLabels.add(instance.triple['label'])
+
+		print setOfLabels
 		#gathers the frequencies in each message
 		#add each word to the setOfWords(vocabulary)
 		currentVocabulary=instance.getFrecuencyTable().getKeys()
@@ -123,18 +128,21 @@ def main():
 		while not queue.empty() and currentCount<numberOfDimensions:
 			pmi=queue.get()[1]
 			
-			if(pmi['pmi']>0.3): #not taking into account the pmi
-				print pmi['word']+"--"+str(pmi['pmi'])+"--"+pmi['label']
+			if(pmi['pmi']>-2): #not taking into account the pmi
+				#print pmi['word']+"--"+str(pmi['pmi'])+"--"+pmi['label']
 				currentCount=currentCount+1
 				setOfSelectedWords.add(pmi['word'])
 
 
-	#train a set of Classifiers
+	#train a set of Classifiers for words
 	print "training classifiers"
 	#setOfClassifiers=trainPredictors(listOfData,setOfSelectedWords,setOfWords)
 	
 
 	#once the classifiers are trained get the
+
+	#creates a file for fpgrowth
[…]

### 2012-08-29 main.py
Finished SVM supervised learning approach

@@ -66,7 +66,7 @@ def main():
 	#Read the file and convert triples into objects
 	
 	#read file with messages
-	listOfTriples=readCSV("Data/sonyReduced.csv")
+	listOfTriples=readCSV("Data/terraReducedTest.csv")
 	
 	listOfData=[]
 	#convert the triples to objects
@@ -128,7 +128,7 @@ def main():
 		while not queue.empty() and currentCount<numberOfDimensions:
 			pmi=queue.get()[1]
 			
-			if(pmi['pmi']>-2): #not taking into account the pmi
+			if(pmi['pmi']>0.2): #not taking into account the pmi
 				#print pmi['word']+"--"+str(pmi['pmi'])+"--"+pmi['label']
 				currentCount=currentCount+1
 				setOfSelectedWords.add(pmi['word'])
@@ -210,16 +210,14 @@ def main():
 
 
 	#this defines the number of seeds(annotated data for the algorithm)
-	percentageOfSeeds=0.1
-	numberOfSeeds=len(instanceVectors)*0.1
-	currentNumberOfSeeds=0
+	
 	
 	currentNumberOfSeedsPerLabel={}
 	for key in setOfLabels:
 		currentNumberOfSeedsPerLabel[key]=0
 
 	#there should be an equal number of seeds for each label
-	percentage=0.9
+	percentage=0.1
 	numberOfSeeds=len(instanceVectors)*percentage
 	currentNumberOfSeeds=0
 
@@ -277,15 +275,22 @@ def main():
 			
 			prediction=listOfClassifiers[label].predict(testMatrix[i])[0]
 			print "predicttion of:: "+label+":"+str(prediction)+"__real:"+testListOfdata[i].triple['label']
+			countOfPredictions=countOfPredictions+1
 			if(prediction==1.0):
-				countOfPredictions=countOfPredictions+1
+				
 				print "predicted:: "+label+"__real:"+testListOfdata[i].triple['label']
 				if(label==testListOfdata[i].triple['label']):
 					countOfRightClassifications=countOfRightClassifications+1
+			else:
+				
+				print "predicted:: "+label+"__real:"+testListOfdata[i].triple['label']
+				if(label!=testListOfdata[i].triple['label']):
+					countOfRightClassifications=countOfRightClassifications+1
 
+	print "len of testdata:"+str(len(testListOfdata))
 	print "right class:"+str(countOfRightClassifications)
[…]

### 2012-08-29 docs/paper.tex
Finished semisupervised Approach

@@
 Learning Seminar\\ Saarland University}
-\title{Short Text Topic Classification using Label Propagation}
+\title{Topic Classification of short product Reviews using Label Propagation}
 \begin{document}
@@
 \\
-In respect to short text classification X proposes [xxxxreferencesherexxxx] to do Feature Extension to deal with data sparcity, in his approach each comment is extended with extra words from an expansion vocabulary.
-[Overcoming the Brittleness Bottleneck using Wikipedia:
-Enhancing Text Categorization with Encyclopedic Knowledge] proposes on the other hand to use enciclopedic knowledge from wikipedia for extending the short commetns.
-As opposed to ~\cite{Sun:2012:STC:2348283.2348511} who reduces even more the word space of the comments by using information retrieval voting schemes.\\
+In respect to short text classification ~\cite{Fan:2010:NMC:1916732.1917677} proposes  to do Feature Extension to deal with data sparcity, in his approach each comment is extended with extra words from an expansion vocabulary.\\
+~\cite{Gabrilovich:2006:OBB:1597348.1597395} proposes on the other hand to use encyclopedic knowledge from wikipedia for extending the short comments.\\
+As opposed to the above ones  ~\cite{Sun:2012:STC:2348283.2348511} reduces the word space of the comments to keywords and use information retrieval with a voting scheme to find labels for short comments.\\
 \\

### 2012-08-29 IO/csvReader.py

@@ -42,6 +42,8 @@ def readCSV(path):
 			triple['label']=row[indexLabel2].replace(" ","_")
 		else:
 			triple['label']=row[indexLabel1].replace(" ","_")
+		triple['label']=triple['label'].lower()
+		triple['label']=triple['label'].strip()
 		triple['polarity']=row[indexPolarity]
 
 		listOfTriples.append(triple)

### 2012-08-29 IO/data.py

@@ -6,6 +6,7 @@ class Instance:
 
 	def __init__(self,triple):
 		self.triple=triple
+		
 		self.vector=[]
 
 	#change the message in the triple,cleaning it
@@ -15,6 +16,9 @@ class Instance:
 		
 		#remove stopwords,make words lowercase
 		self.triple['message']=processing.cleaning.removeStopWords(self.triple['message'])
+
+		#remove acceptns
+		self.triple['message']=processing.cleaning.removeAccents(self.triple['message'])
 		
 		return 1
 

### 2012-08-29 processing/cleaning.py

@@ -78,6 +78,9 @@ def removeStopWords(message):
 	p = re.compile( '|')
 	message=p.sub("",message)
 
+	p = re.compile( '(!)+')
+	message=p.sub("",message)
+
 	newMessage=""
 	
 	

### 2012-08-29 utils/wordPredictor.py

@@ -16,7 +16,7 @@ class wordPredictor:
 		prob = svm_problem( trainingLabels,trainingSet)
 		
 		#actual classifier
-		self.predictor=svm_train(prob, '-t 2 -c 1')
+		self.predictor=svm_train(prob, '-t 1 -c 2 -g 1.2 -d 5')
 
 	#instance is an array [dimension1, dimension2..]
 	#predicts the label for an instance
@@ -24,6 +24,48 @@ class wordPredictor:
 		predicted_labels, _, _= svm_predict([1],[instance],self.predictor)
 		return predicted_labels
 
+#intances= set of instances
+#setOfLabels= set of labels
+#trains N classifiers for predicting each of the labels in SetOfLabels
+#returns a dictionary. Key: word, value: wordPredictor
+def trainSVMPredictoForLabels(instanceVectors,setOfLabels,matrix):
+	dictionaryOfPredictors={}
+	count=0
+	for label in setOfLabels:
+
+		print "training predictor for:"+label
+		print str(count+1) + "-out of-"+ str(len(setOfLabels))
+		count=count+1
+		trainingSet=[]
+		trainingLabels=[]
+		for i in range(0,len(instanceVectors)):
+			instance=instanceVectors[i]
+			currentLabel=instance.triple['label']
+			if label==currentLabel:
+				trainingLabels.append(1.0)
+			else:
+				trainingLabels.append(0.0)
+
+			trainingSet.append(matrix[i])
+		dictionaryOfPredictors[label]=wordPredictor(trainingSet,trainingLabels)
+		rightPredictions=0
+		for i in range(0,len(instanceVectors)):
+			instance=instanceVectors[i]
+			currentLabel=instance.triple['label']
+
+
+			prediction=dictionaryOfPredictors[label].predict(matrix[i])[0]
+			if label==currentLabel:
+				
+				#print "positive (?) prediction: "+ str(prediction)
+				if(1.0==prediction):
+					rightPredictions=rightPredictions+1
+			else:
+				#print "negative (?) prediction: "+ str(prediction)
+				if(0.0==prediction):
+					rightPredictions=rightPredictions+1
+		print "***********************presition***:"+str(rightPredictions/(len(instanceVectors)*1.0))
+	return dictionaryOfPredictors
 
 
 #intances= set of instances
@@ -64,6 +106,8 @@ def trainPredictors(instances,setOfWords,vocabulary):
 		for instance in instances:
[…]

### 2012-08-29 main.py
Added support for semisupervised

@@ -58,7 +58,7 @@ def createJuntoGraph(path,instanceVectors,matrixLSA):
 			juntoGraphFileContent=juntoGraphFileContent+str(i)+"\t"+str(j)+"\t"+str(distanceValue)+"\n"
 	graphFile.write(juntoGraphFileContent)
 
-def main():
+def trainSupervisedSVM():
 
 	#table frquencuency of all the words in the messages
 	frecuencies=frecuencyTable()
@@ -346,8 +346,288 @@ def  justGenerateSeeds(percentage):
 	
 
 
+def trainSemisupervisedSVM():
+	print "training semi-supervised"
+	#table frquencuency of all the words in the messages
+	frecuencies=frecuencyTable()
+	
+	#Read the file and convert triples into objects
+	
+	#read file with messages
+	listOfTriples=readCSV("Data/terraReduced.csv")
+	
+	listOfData=[]
+	#convert the triples to objects
+	for triple in listOfTriples:
+		listOfData.append(Instance(triple))
+		
+	#stores the vocabulry  of the docs
+	setOfWords=Set()
+	#stores the set of labels found in the instnaces
+	setOfLabels=Set()
+	for instance in listOfData:
+		print "cleaning: "+str(instance.triple['id'])
+
+		#stores the labels
+
+
+		#clean message
+		instance.cleanMessage()
+		instance.measureFrequencies()
+
+		if(instance.triple['label']!=None and instance.triple['label']!=''):
+			setOfLabels.add(instance.triple['label'])
+
+		print setOfLabels
+		#gathers the frequencies in each message
+		#add each word to the setOfWords(vocabulary)
+		currentVocabulary=instance.getFrecuencyTable().getKeys()
+		for v in currentVocabulary:
+			setOfWords.add(v)
+
+		for word in instance.triple['message'].split(" "):
+			frecuencies.add(word)
+
+	listOfWordsByValue=frecuencies.sort_by_value()
+	print "words by frequencie---"
+	for wordd in listOfWordsByValue:
+		print wordd
+	print "--------------------------"
+
+	print "looking for PMI"
+	#get the instances which are annotated
+	listOfAnnotatedData=[]
+	listOfUnnanotatedData=[]
+	for instance in listOfData:
+		if instance.triple['label']!="":
+			listOfAnnotatedData.append(instance)
+		else:
+			listOfUnnanotatedData.append(instance)
+
[…]

### 2012-08-29 main.py
Added parameters to the functions

@@ -58,7 +58,7 @@ def createJuntoGraph(path,instanceVectors,matrixLSA):
 			juntoGraphFileContent=juntoGraphFileContent+str(i)+"\t"+str(j)+"\t"+str(distanceValue)+"\n"
 	graphFile.write(juntoGraphFileContent)
 
-def trainSupervisedSVM():
+def trainSupervisedSVM(pathOfDataFile,percentageOfSamples,pmiLowerBound):
 
 	#table frquencuency of all the words in the messages
 	frecuencies=frecuencyTable()
@@ -66,7 +66,8 @@ def trainSupervisedSVM():
 	#Read the file and convert triples into objects
 	
 	#read file with messages
-	listOfTriples=readCSV("Data/terraReducedTest.csv")
+	#Data/terraReducedTest.csv
+	listOfTriples=readCSV(pathOfDataFile)
 	
 	listOfData=[]
 	#convert the triples to objects
@@ -128,7 +129,7 @@ def trainSupervisedSVM():
 		while not queue.empty() and currentCount<numberOfDimensions:
 			pmi=queue.get()[1]
 			
-			if(pmi['pmi']>0.2): #not taking into account the pmi
+			if(pmi['pmi']>pmiLowerBound): #not taking into account the pmi
 				#print pmi['word']+"--"+str(pmi['pmi'])+"--"+pmi['label']
 				currentCount=currentCount+1
 				setOfSelectedWords.add(pmi['word'])
@@ -217,7 +218,7 @@ def trainSupervisedSVM():
 		currentNumberOfSeedsPerLabel[key]=0
 
 	#there should be an equal number of seeds for each label
-	percentage=0.1
+	percentage=percentageOfSamples
 	numberOfSeeds=len(instanceVectors)*percentage
 	currentNumberOfSeeds=0
 
@@ -346,7 +347,7 @@ def  justGenerateSeeds(percentage):
 	
 
 
-def trainSemisupervisedSVM():
+def trainSemisupervisedSVM(pathOfDataFile,percentageOfSamples,pmiLowerBound):
 	print "training semi-supervised"
 	#table frquencuency of all the words in the messages
 	frecuencies=frecuencyTable()
@@ -354,7 +355,7 @@ def trainSemisupervisedSVM():
 	#Read the file and convert triples into objects
 	
 	#read file with messages
-	listOfTriples=readCSV("Data/terraReduced.csv")
[…]

### 2012-08-30 main.py
Added precision/recall for each label

@@ -267,10 +267,21 @@ def trainSupervisedSVM(pathOfDataFile,percentageOfSamples,pmiLowerBound):
 
 	#train an svm classifier for the given samples
 	print "len of training data:"+str(len(trainingListOfdata))
+	#pair of positivePredictions, numberOfPredictions
+	numberOfSamplesPerLabel={}
+	dictOfPresicion={}
+
+
+	for label in setOfLabels:
+		numberOfSamplesPerLabel[label]=0
+		dictOfPresicion[label]=[0,0]
+
 	listOfClassifiers=trainSVMPredictoForLabels(trainingListOfdata,setOfLabels,trainingMatrix)
 	countOfRightClassifications=0
 	countOfPredictions=0
+	notClassified=0
 	for i in range(0, len(testListOfdata)):
+		numberOfSamplesPerLabel[testListOfdata[i].triple['label']]=numberOfSamplesPerLabel[testListOfdata[i].triple['label']]+1
 		for label in setOfLabels:
 			
 			
@@ -278,10 +289,12 @@ def trainSupervisedSVM(pathOfDataFile,percentageOfSamples,pmiLowerBound):
 			print "predicttion of:: "+label+":"+str(prediction)+"__real:"+testListOfdata[i].triple['label']
 			countOfPredictions=countOfPredictions+1
 			if(prediction==1.0):
-				
+				dictOfPresicion[label][1]=dictOfPresicion[label][1]+1
 				print "predicted:: "+label+"__real:"+testListOfdata[i].triple['label']
 				if(label==testListOfdata[i].triple['label']):
+					dictOfPresicion[label][0]=dictOfPresicion[label][0]+1
 					countOfRightClassifications=countOfRightClassifications+1
+					
 			else:
 				
 				print "predicted:: "+label+"__real:"+testListOfdata[i].triple['label']
@@ -292,6 +305,18 @@ def trainSupervisedSVM(pathOfDataFile,percentageOfSamples,pmiLowerBound):
 	print "right class:"+str(countOfRightClassifications)
 	print "number of predctions:"+str(countOfPredictions)
 	print "accuracy: "+str(countOfRightClassifications/(countOfPredictions*1.0))
+
+	print "-----------------------"
+	for label in setOfLabels:
+		if(numberOfSamplesPerLabel[label]>0):
+			print "***"+label+"***"
+			if(dictOfPresicion[label][1]>0):
[…]

### 2012-08-30 main.py
Addded support for commandline

@@ -1,7 +1,7 @@
 #author: David Przybilla
 #date: July 2012
 #this file is the main of the app
-
+import sys
 from IO.csvReader import readCSV
 from IO.data import Instance
 from IO.data import getSetOfWordsPerLabel
@@ -11,6 +11,7 @@ from processing.LatentSemantic import *
 from math import sqrt
 from math import floor
 from math import cos
+from math import ceil
 from math import degrees
 from  Queue import PriorityQueue
 from utils.wordPredictor import wordPredictor
@@ -116,11 +117,65 @@ def trainSupervisedSVM(pathOfDataFile,percentageOfSamples,pmiLowerBound):
 			listOfAnnotatedData.append(instance)
 		else:
 			listOfUnnanotatedData.append(instance)
+	currentNumberOfSeedsPerLabel={}
+	for key in setOfLabels:
+		currentNumberOfSeedsPerLabel[key]=0
 
-	listOfPMI=getSetOfWordsPerLabel(setOfLabels,setOfWords,listOfAnnotatedData,"PMI")
+	#there should be an equal number of seeds for each label
+	percentage=percentageOfSamples
+	numberOfSeeds=len(listOfData)*percentage
+	currentNumberOfSeeds=0
+
+	numberOfSeedsPerLabel=math.floor(numberOfSeeds/(1.0*len(setOfLabels)))
+	numberOfSeeds=numberOfSeedsPerLabel*len(setOfLabels)
+	listForAuxiliaryTraining=[]
+	listOfTrainingData_=[]
+	SetOfSeeds2=Set()
+	for instance in listOfData:
+		if ( (not instance.triple['label']=='') and (not instance.triple['label']==None) ):
+			#if the instance is between the first 1000 then it is  a seed otherwise it is test
+			if(currentNumberOfSeedsPerLabel[instance.triple['label']]<numberOfSeedsPerLabel and  not instance.triple['message'] in SetOfSeeds2):
+				currentNumberOfSeedsPerLabel[instance.triple['label']]=currentNumberOfSeedsPerLabel[instance.triple['label']]+1
+				SetOfSeeds2.add(instance.triple['message'])
+				listOfTrainingData_.append(instance)
+			else:
+				listForAuxiliaryTraining.append(instance)
+		
+
+
[…]

### 2012-08-30 docs/paper.tex
Added introduction ,dataset

@@
 \\
-In this paper a semisupervised technique is used in order to label the topic of a set of comments 
-related to a product or service.\\
-The semi supervised techniques presents two advantages.\\
-First by using semisupervised methods the amount of neccessary annotateed data is less,
-and second the unlabeled data is used during training, this is important since the amount of unlabeled data in these tasks is abundant and available.\\
+In the Scenario of text classification Semi-supervised techniques present two advantages:\\
+First a semi-supervised method should allow to classify text by annotating only a small portion of data,thus reducing the labor of annotating.\\
+Second the unlabeled data is used during training, this is important since the amount of unlabeled data in these tasks is abundant and available, therefore it can be used to provide extra knowledge to the model.\\
 \\
-
+In ~\cite{Ando:2005:FLP:1046920.1194905} propose a semi-supervised approach using linear classifiers for multiple learning tasks.\\
+They proposed to create additional classifications tasks (Auxiliary Problems) aside from the Target Problem.\\
+The underlying idea is that the auxiliary problems will help finding good predictors.\\
+One of the constraints in this approach is that auxiliary problems should be  able to automatically generate labelled data from the original unlabeled data.\\
+\\
+In contrast ~\cite{Zhu:2005:SLG:1104523} proposes a graph approach called label propagation for
+doing semi-supervised learning.\\
+This approach maps the data to a graph representation, then labelled instances propagate their labels through the graph, allowing unlabelled data to adopt the label of those instances which are similar.\\
+\\
 Though Classifying text has been a widely studied topic,the focus has been on long documents,
@@
 \\
-In this paper, a Semisupervised technique called Label propagation is used
-in order to label a set of tweets about product reviews.\\
-Label propagation is reviewed in part X.\\
-Since data sparcity showed to be a problem a way for handling it
-is discuss in in part Y using an approach Z.\\
-The results are given in the part W.\\
-The source code of the implementation is available at \url{https://github.com/dav009/LPForTopicIdentification},the datasets however are not public, since they are constrained by a permission license.
+This paper describes the setup of an experiment for classifying short-text comments of product reviews extracted from twitter.\\
+Two semi-supervised techniques are used, Label Propagation ~\cite{Zhu:2005:SLG:1104523}  and  a variation of Structural learning problem for multitasks ~\cite{Ando:2005:FLP:1046920.1194905}.\\
+The next sections describe briefly each of the proposed methods and how they were adapted to the task, then the pre-processing involved. \\
+Addionally the results are shown, where both methods are compared among themselves and to a supervised approach.
+Finally a short conclusion and future work are discussed.\\
+\\
+The source code of the implementation is available at github\footnote{\url{https://github.com/dav009/LPForTopicIdentification}},the datasets however are not public, since they are constrained by a permission license.
+
+\part*{Datasets}
+The Datasets of this experiments were provided by Meridean.\\
+Meridean\footnote{\url{http://http://merideangroup.com/}} is a Colombian company which extracts tweets
+mentioning latinamerican companies or products.\\
+\\
+The datasets are separated by product.\\
+There are 3 datasets in this experiment:
+\begin{itemize}
+	\item Clothing-Brand dataset
+	\item Mobile-Phone dataset
+	\item hygienic-product dataset
+\end{itemize}
+
+Each dataset is composed of tuples,each tuple contains : the source of the opinion, the opinion, the polarity and the topic.\\
+
+\begin{table}[h]
+\centering
+\begin{tabular}{| l |}
+\hline
+\textbf{Message:}\\
+$\#$ProbandoXperiaArcS Gracias @TalkMex.\\
+Las fotos se ven tan nitidas.\\
+\hline
+\textbf{Translation:}\\
+$\#$TestingXperiaArcs Thanks to @TalkMex.\\
+Pictures are very sharp.\\
+\hline
+\textbf{Topic:}\\
+Camera\\
+\hline
+\end{tabular}
+\caption{Sample Tuple}
+\label{tab:sampleTuple}
+\end{table}
 
@@
 \part*{Experiment}
-Meridean [reference to meridean] is a Colombian company which extracts and saves tweets
-mentioning latinamerican companies or products.\\
-Basically they mine  tweets and offer sentiment analysis services to companies.\\
-The range of products reviews go from Electronic Devices to Sanitary Products.\\
-\\
-The experiment use two of their Collections of product reviews.\\
-The first DataSet review a mobilephone, the second dataset review a Sanitary product.\\
-\\
+
 La

### 2012-08-30 docs/paper.tex
Added content for labelPropagation

@@
 This approach maps the data to a graph representation, then labelled instances propagate their labels through the graph, allowing unlabelled data to adopt the label of those instances which are similar.\\
+~\cite{Speriosu_twitterpolarity} uses Label Propagation for doing Polarity Classification on tweets.\\
 \\
@@
 
-Since the datasets used in this experiment are real data crawled from twitter and other sources there is a lot of noise in them.\\
+The Datasets used in this experiment are actual data crawled from twitter and other sources, therefore there is a lot of noise in them.\\
 Some of the problems are (but not limited) to:\\
@@
 	\item Internet Language, replacing some letters for others whose phonetics are similar i.e: ``\textbf{qu}iero" (I want) for ``\textbf{k}iero", abbreviations and expressions (``Jaja'' ``jiji" ... )
-	\item Twitter Jargon such as: ``RT:",``@", hashtags and mentions. 
+	\item Twitter Jargon such as: ``RT:",``@"..
 \end{itemize}
 
-The preprocessing done was the following:
+The pre-processing done was the following:
 \begin{enumerate}
@@
 
+When it comes to pre-processing there could be wide number of possible 
+tasks that can be done, I try to keep it simple given the time constraints. \\
+\\
+As a result of this pre-processing each comment is converted into a bag of keywords.\\
+This will be later transform into a vector space representation.
+
+%% for future work mention that words like 'camera' that turn out to be good predictor, can be biased by the fact that is misswritten 'camera '  'cmarea'
+
 \part*{Label Propagation}
 
+This Semi-supervised learning graph method was proposed by Zhu ~\cite{Zhu:2005:SLG:1104523}.\\
+The idea behind Label propagation is similar to K-Neighbors, nevertheless Label propagation make use of the unlabeled data during the training process.\\
+
+This approach maps the data to a graph representation.
+In this representation each Arc of the graph will connect two nodes only if the two nodes are similar,
+and the weights of the arcs are directly proportional to the similarity of the incident nodes.\\
+
+With respect to our classification task,each node in the graph corresponds to the feature vector of a comment.
+The weights of the arcs are given by the cosine distance among the vectors.\\
+The final representation is a complete graph.\\
+\\
+In the LP algorithm, the label information of any
+vertex in a graph is propagated to nearby vertices
+through weighted edges until a global stable stage is
+achieved.~\cite{Chen:2006:REU:1220175.1220192}.
+If a weight arc is high, the label will travel easier.\\
+\\
+
+\part*{Structure Learning}
+A Semi-supervised learning method proposed in ~\cite{Ando:2005:FLP:1046920.1194905}.\\
+
 \part*{Feature Generation}
-\part*{Structure Learning}
 

### 2012-08-31 docs/paper.tex
Added Structural Learning part

@@
 
-\author{David Przybilla\footnote{dav.alejandro@gmail.com , davida@coli.uni-saarland.de}\\ Term Paper for Unsupervised Semisupervised
-Learning Seminar\\ Saarland University}
-\title{Topic Classification of short product Reviews using Label Propagation}
+\author{David Przybilla\\dav.alejandro@gmail.com, davida@coli.uni-saarland.de\\ \\ Term Paper for Unsupervised Semi-supervised
+Learning Seminar\\ Universit\"{a}t des Saarlandes}
+\title{Classification of short product Reviews using Semi-Supervised Learning}
 \begin{document}
@@
 
-\part*{Introduction}
+\section{Introduction}
 Twitter and Tuenti are popular microblogging services in Latinamerica,
@@
 \\
-In ~\cite{Ando:2005:FLP:1046920.1194905} propose a semi-supervised approach using linear classifiers for multiple learning tasks.\\
+In ~\cite{Ando:2005:FLP:1046920.1194905} Zhang and Kubota proposed a semi-supervised approach using linear classifiers for multiple learning tasks.\\
 They proposed to create additional classifications tasks (Auxiliary Problems) aside from the Target Problem.\\
-The underlying idea is that the auxiliary problems will help finding good predictors.\\
-One of the constraints in this approach is that auxiliary problems should be  able to automatically generate labelled data from the original unlabeled data.\\
+The underlying idea is that the auxiliary problems will help finding good predictive structures.\\
+One of the constraints in this approach is that auxiliary problems should be  able to automatically generate labelled data from the original unlabeled data.
+This method has been used in tasks such as Text Chunking ~\cite{Ando:2005:HSL:1219840.1219841}\\
 \\
@@
 whereas tweets are at most 144 characters long.\\
-The new trends in these social networks have led to research about classification in short texts, the latter has  shown that it arises new challenges, and previous approaches are not  effective.\\
-One of the reasons is that  user generated comments in the mentioned services tend to be extremly short, leading to sparce feature representations.\\
+The new trends in these social networks have led to research about classification in short texts, the latter has  shown that it arises new challenges, and former approaches are not  effective.\\
+One of the reasons is that  user generated comments in the mentioned services tend to be extremely short, leading to sparce feature representations.\\
 \\
@@
 ~\cite{Gabrilovich:2006:OBB:1597348.1597395} proposes on the other hand to use encyclopedic knowledge from wikipedia for extending the short comments.\\
-As opposed to the above ones  ~\cite{Sun:2012:STC:2348283.2348511} reduces the word space of the comments to keywords and use information retrieval with a voting scheme to find labels for short comments.\\
+As opposed to the above ones,  ~\cite{Sun:2012:STC:2348283.2348511} reduces the word space of the comments to keywords and use information retrieval with a voting scheme to find labels for short comments.\\
 \\
@@
 
-\part*{Datasets}
+\section{Datasets}
 The Datasets of this experiments were provided by Meridean.\\
@@
 \hline
-\textbf{Message:}\\
+\textbf{Comment:}\\
 $\#$ProbandoXperiaArcS Gracias @TalkMex.\\
@@
 \end{tabular}
-\caption{Sample Tuple}
+\caption{Sample Comment}
 \label{tab:sampleTuple}
@@
 
-\part*{Pre-processing}
+\section{Pre-processing}
 
@@
 
-\part*{Label Propagation}
+\section{Label Propagation}
 
@@
 In this representation each Arc of the graph will connect two nodes only if the two nodes are similar,
-and the weights of the arcs are directly proportional to the similarity of the incident nodes.\\
+the weights of the arcs are directly proportional to the similarity of the incident nodes.\\
 
@@
 In the LP algorithm, the label information of any
-vertex in a graph is propagated to nearby vertices
-through weighted edges until a global stable stage is
-achieved.~\cite{Chen:2006:REU:1220175.1220192}.
-If a weight arc is high, the label will travel easier.\\
+node in a graph is propagated to nearby nodes
+through weighted arcs until a global stable stage is
+achieved ~\cite{Chen:2006:REU:1220175.1220192}.
+If a weight arc is high, the label will travel easier through the graph.\\
 \\
+The LP Algorithm iterates until convergence,
+at each step the algorithm will push the labels
+of the labeled data points through the arcs of high weights.The underlying assumption is that instances among a class will have high weighted arcs
+connecting them.\\
+At each iteration the labels of the labelled data are clamped.\\
 
-\part*{Structure Learning}
+This propagation is done by measuring a transition matrix $T$.
+The transition matrix states the probability of propagating the label of an instance,
+and it is measured from the weights of the arcs of the graph.\\
+\\
+Let $T_{ij}$ be the probability of propagating the label of instance $i$ to instance $j$, then it can be defined as:\\
+\begin{align}
+	T_{ij}=P(i \rightarrow j)=\frac{w_{ij}}{\sum_{k=1}^{n} w_{kj}}
+\end{align}
+
+\subsection{Algorithm}
+Let $Y_{ij}$ be the soft probability of labeling instance $i$ with label $j$.\\
+\\
+Given our semi-supervised task, then $Y$ can be divided into:\\
+\\
+$Y_{U}$:the soft labels for the unlabelled data\\
+$Y_{L}$:the soft labels for the labelled data\\
+\\
+This means that $Y_{L}$ is given at the beginning of the problem
+and the target is to find good values for $Y_{U}$.\\
+\\
+\textbf{Step 1 - Init}: In this step, the Labels for $Y_{L}$ are clamped, and the labels for $Y_{U}$ are randomly initialized.\\
+The proof that the initialization values of $Y_{U}$ are not transcendental can be found at ~\cite{Zhu:2005:SLG:1104523}.\\
+\\
+\textbf{Step 2 - Propagation}: In this step, the Labels of neighbouring nodes are pushed.\\
+Let $t$ be the current iteration, then $Y^{t+1}$ is defined as:
+\begin{align}
+Y^{t+1} = T Y^{t}
+\end{align}
+\\
+\textbf{Step 3 - Clamp Labelled Data}: In this step, the Labels for $Y_{L}$ are clamped.\\
+\\
+\textbf{Step 4 - Repeat}: Repeat from step 2 until convergence.\\
+\\
+\textbf{Step 5 - Labeling Approach}: Once there is convergence, a label has to be chosen for each node in the graph, there is more than one approach.\\
+The simplest approach would be to pick the label with the highest probability. \\
+In ~\cite{Zhu:2005:SLG:1104523} there is an empirical analysis on more sophisticated approaches, there it is shown how this criteria can affect the performance, nevertheless for this experiment the simple approach was used.\\
+\\
+To summarize, in the experiment we convert our data into a complete graph,
+each node is the feature vector of a comment, and the weight of each arc
+corresponds to the similarity of the comments being incident to the arc.\\
+This Graph is  fed to the Label Propagation Algorithm.
+
+\section{Structure Learning}
 A Semi-supervised learning method proposed in ~\cite{Ando:2005:FLP:1046920.1194905}.\\
+This paper proposes a way to learn multiple classification tasks.In this approach the original Classification Task(Target Problem) is extended by creating a set of auxiliary classification tasks.\\
+The Auxiliary Classification tasks are used to improve performance on the target task,
+the underlying assumption is that by solving the auxiliary problems one should be able to find good predictive structures.\\
+The Auxiliary Tasks are trained on the unlabeled data,in consequence one constraint to the creation of auxiliary tasks is that they should be able to automatically generate training data from the target's problem unlabelled data.In ~\cite{Ando:2005:HSL:1219840.1219841} it is argued that having a high number of auxiliary tasks is beneficial for the performance.\\
+\\
+In this paper's experiment, the target task corresponds to find the label of each comment.\\
+The auxiliary problems are defined as:\\
+Learn a linear predictor using the Unlabelled data for the $K$ most common words in the unlabeled data and a predictor for the words with highest Pointwise mutual information(PMI) from the Labelled Data.\\
+\\
+For learning this tasks, first the Words with highest PMI are found using the labelled data, then the words with highest frequency in the unlabelled data are found.\\
+Subsequently a linear classifier for predicting each of this words is trained using the unlabelled data.
+It is clear that labels for this tasks can be easily generated by masking the words for which the classifiers are being trained from the comments.\\
+\\
+By solving the auxiliary tasks, the feauture vectors of the training data for the target problem can be extended with the predictions of the auxiliary tasks.\\
+This might shown useful in the setup of the experiment, since we are extending the feauture representations from knowledge of unlabelled data.\\
+\\
+Finally a linear classifier is learnt using the training data for the target problem.
 
-\part*{Feature Generation}
+\section{Feature Generation}
 
-\part*{Experiment}
+\section{Experiment}
+For the experiments, the three datasets mentioned above were used as training and test data.\\
+The experiments corresponds to the following:
+\begin{itemize}
+	\item Single task Supervised Learning using SVM (SVM)
+	\item Single task Semi-supervised Learning using Label Propagation (LP)
+	\item Single task Semi-supervised Learning using Structural Learning(Single-SL)
+	\item Multitask Semi-supervised Learning using Structural Learning(Multi-SL)
+\end{itemize}
+
+An OpenSource implementation of Label Propagation was used $Junto$\footnote{ \url{https://github.com/parthatalukdar/junto} }.\\
+\\
+For SL, the libsvm\footnote{\url{http://www.csie.ntu.edu.tw/~cjlin/libsvm/}} library provided an implementation for training SVM.
 
@@
 
-\part*{Results}
+\section{Results}
 
-\part*{Future Work}
+\section{Future Work}
 

### 2012-09-02 docs/paper.tex
Added experiments details

@@
 \begin{itemize}
-	\item Clothing-Brand dataset
+	\item Sportwear dataset
 	\item Mobile-Phone dataset
@@
 \end{table}
+
+Each dataset contains approximately 5000 tuples.
 
@@
 \\
+More sophisticated versions of this approach have been presented and assessed, in ~\cite{Talukdar:2010:EGS:1858681.1858830} Talukdar and Pereira showed an empirical comparison among different variations of the LP algorithm, a modified absortion algorithm is presented where seed labels are not clamped,and it is shown to have better performance in the given tasks.
+Nevertheless within this paper we call LP to the algorithm proposed by Zhu ~\cite{Zhu:2005:SLG:1104523}.\\
+\\
 To summarize, in the experiment we convert our data into a complete graph,
@@
 corresponds to the similarity of the comments being incident to the arc.\\
-This Graph is  fed to the Label Propagation Algorithm.
+This Graph is  fed to the Label Propagation Algorithm proposed by Zhu.\\
 
@@
 \\
-Finally a linear classifier is learnt using the training data for the target problem.
+Finally a linear classifier is learnt using the training data for the target problem.\\
+With respect to the ASO-SVD algorithm, this paper just explore a naive approach by using auxiliary problems, in this regard the auxiliary classifiers are used to extend the feature vectors.
 
@@
 \begin{itemize}
-	\item Single task Supervised Learning using SVM (SVM)
-	\item Single task Semi-supervised Learning using Label Propagation (LP)
-	\item Single task Semi-supervised Learning using Structural Learning(Single-SL)
-	\item Multitask Semi-supervised Learning using Structural Learning(Multi-SL)
+	\item Single task Supervised Learning using SVM ($SVM$)
+	\item Single task Semi-supervised Learning using Label Propagation ($LP$)
+	\item Single task Semi-supervised Learning using The naive Structural Learning($SL$)
+
 \end{itemize}
 
-An OpenSource implementation of Label Propagation was used $Junto$\footnote{ \url{https://github.com/parthatalukdar/junto} }.\\
+Each of the experiments were ran with different amounts of training data, specifically 10\%, 30\%, 60\% and 90\%\\
 \\
-For SL, the libsvm\footnote{\url{http://www.csie.ntu.edu.tw/~cjlin/libsvm/}} library provided an implementation for training SVM.
+For the Label Propagation  $Junto$ \footnote{ \url{https://github.com/parthatalukdar/junto} } ~\cite{Talukdar:2010:EGS:1858681.1858830} was used.
+$Junto$ is an open source implementation of the Label Propagation algorithm proposed by Zhu.\\
+\\
+For $SL$ and $SVM$ the libsvm\footnote{\url{http://www.csie.ntu.edu.tw/~cjlin/libsvm/}} library provided an implementation for training SVM.\\
+For all the linear classifiers trained in the experiments a  polynomial Kernel was picked and the value of $gamma$ was 1.2, the reason behind this choice is motivated by the empirical results obtained by ~\cite{Joachims:1998:TCS:645326.649721} in a similar task.
 
@@
 \section{Future Work}
+%other LP variations ( MAD for noisy ..)
+%multitask
+%more feautures for running
+%extending the comments with extra knowledge
+%better preprocesing
 

### 2012-09-03 docs/paper.tex
Added graphics adn results

@@
 Finally a linear classifier is learnt using the training data for the target problem.\\
-With respect to the ASO-SVD algorithm, this paper just explore a naive approach by using auxiliary problems, in this regard the auxiliary classifiers are used to extend the feature vectors.
+With respect to the ASO-SVD algorithm, this paper just explore a naive approach by using auxiliary problems, in this regard the auxiliary classifiers are used to extend the feature vectors.\\
+For the rest of the paper we will refer to this approach as Naive SL.
 
@@
 For $SL$ and $SVM$ the libsvm\footnote{\url{http://www.csie.ntu.edu.tw/~cjlin/libsvm/}} library provided an implementation for training SVM.\\
-For all the linear classifiers trained in the experiments a  polynomial Kernel was picked and the value of $gamma$ was 1.2, the reason behind this choice is motivated by the empirical results obtained by ~\cite{Joachims:1998:TCS:645326.649721} in a similar task.
+For all the linear classifiers trained in the experiments a  polynomial Kernel was picked and the value of $gamma$ was 1.2, the reason behind this choice is motivated by the empirical results obtained by ~\cite{Joachims:1998:TCS:645326.649721} in a similar task.\\
+\\
+For making the tasks suitable for the given computational power, a subset of the size of $\frac{1}{4}$ of each of the given datasets was used, this has a major drawback, since the more the data the better the behavior of the semi-supervised algorithms.
+Also an upper bound on the number of auxiliary classifiers created by  the naive structure learning was imposed, the auxiliary problems would be 40\% of the most common words in the unlabeled data and the words with highest PMI from the Labelled data.\\
+A major drawback of Label Propagation from a running time perspective is having to calculate a complete graph containing the similarity among the nodes.Calculating a graph with 2 or more millions of arcs consume lots of resources.
+\section{Results}
+In the following subsections, the results for each dataset are described.\\
+\\
+In overall the Naive SL could maintain the f-score given by the Supervised approach, in some cases was able to get a much better f-score by improving recall, in some other cases a slightly better recall resulted in a decline of the precision thus leading to a worse f-score.\\
+\\
+The LP approach on the other hand raised in labels where both of the previous approaches failed such as with the label $Resistance$  in the sportwear dataset Figure~\ref{fig:nike_90_fscore} or $Brand$ $Support$ Figure~\ref{fig:nike_10_fscore},  $Tenderness$  in the Hygienic Product dataset Figure~\ref{fig:terra_30_fscore}, and many others like $Photography$,$Screen$ and $Social$ $Networks$ in the Mobilephone dataset Figure~\ref{fig:sony_30_fscore_more}.\\
+\\
+The Hygienic Product and Sportwear datasets give some decent results, whereas the Mobile Phone dataset shown to be more challenging.\\
+\\
+One factor that might have affected the overall performance was using a subset of the data, this specially seems to affect LP.LP profits from abundant unnanotated data, my hypothesis is that using a very small set of seeds with a large number of unnanotated data should improve the scores given below.\\
+The reason for LP giving such low scores  on some of the tasks might be : first because of the limited number of data, there are some disconnected segments of the graph, therefore a proper propagation cannot be carried out successfully for prediction.\\
+Second the feature vectors are very sparce, leading to the problem mentioned above.\\
+In an attempt to discover whether both more data and selecting more features would benefit the approach  a second test was carried out in the Mobile Phone dataset.
+In this attempt more data were taken into account and a larger number of features were allowed to be part of the feature vectors, the results are given in Figure~\ref{fig:sony_10_fscore_more} and Figure~\ref{fig:sony_30_fscore_more}, in general it can be said that there is much a better f-score for a larger number of labels, so It is possible to speculate that using the whole datasets would double the f-scores given in this report.\\
+\\
 
-La
+Since comments are reduced to a bag of keywords there other factors which could have caused the given results  are:
+\begin{itemize}
+\item Noise,the given data is actual user-generated content thus very noisy.\\
+Noisy data such as miss written words can lead to bad classifications or points isolated in the LP graph.
+Take as an example the label $Camera$ for the Mobile phone dataset, if a good predictor for this label is the actual word ''camera" ,and it is seen in the labelled data, variations such as ''camraa" and others might not result predictive.
 
-\section{Results}
+\item Sparsity and Short Text, feature vectors are very sparce and text is short.
+This could affect in the following ways, lets think again on the label $Camera$ for the Mobile  phone dataset, if we assume we are classifying long texts, an annotated instance can reveal a lot of the topic vocabulary , in this case words such as ''resolution", ''megapixels" and so on.\\
+On the other hand in the short text classification, you got at most 144 characters per text, so you might end up only with a small subset of topic related words.
+For example, lets assume you have a good predictor in your seed set which is the word ''Camera" and ''resolution".
+If there is a message saying just: ''it has a good amount of megapixels", it will be very unlike to be classified correctly, unless there is another entry linking ''megapixels" with one of the predicting words in the seed set.\\
+\\
+With respect to the Topic Vocabulary, I would speculate that this really affect the performance.
+In the Hygenic Product and  Sportwear the terms range are more or less reduced, this is not the case of the mobile phone dataset, the range of topic vocabulary for each label is huge, just take into account the label $Application$, a comment can be given this label if it has a mention to a well known IOS or Android App, such as ''Angry Birds", furthermore take into account the label $Social$ $Network$ where social networks' names are mentioned, on top of that combine all the possible technical words that might appear with the labels $Camera$, $OS$, $Photography$.
+
+\end{itemize}
 
@@
 
+\begin{figure*}[]
+
+  \centering
+    \includegraphics[scale=0.7]{graphics/sportWear/fscore-10-nike}
+    \caption{F-Score, 10\% Training Data, Sportwear dataset}
+   \label{fig:nike_10_fscore}  
+\end{figure*}
+
+\begin{figure*}[]
+
+  \centering
+    \includegraphics[scale=0.7]{graphics/sportWear/fscore-30-nike}
+    \caption{F-Score, 30\% Training Data, Sportwear dataset}
+   \label{fig:nike_30_fscore}  
+\end{figure*}
+
+\begin{figure*}[]
+
+  \centering
+    \includegraphics[scale=0.7]{graphics/sportWear/fscore-60-nike}
+    \caption{F-Score, 60\% Training Data, Sportwear dataset}
+   \label{fig:nike_60_fscore}  
+\end{figure*}
+
+\begin{figure*}[]
+
+  \centering
+    \includegraphics[scale=0.7]{graphics/sportWear/fscore-90-nike}
+    \caption{F-Score, 90\% Training Data, Sportwear dataset}
+   \label{fig:nike_90_fscore}  
+\end{figure*}
+
+\begin{figure*}[]
+
+  \centering
+    \includegraphics[scale=0.7]{graphics/terra/fscore-terra-10}
+    \caption{F-Score, 10\% Training Data,Hygienic Product}
+   \label{fig:terra_10_fscore}  
+\end{figure*}
+
+\begin{figure*}[]
+
+  \centering
+    \includegraphics[scale=0.7]{graphics/terra/fscore-terra-30}
+    \caption{F-Score, 30\% Training Data, Hygienic Product}
+   \label{fig:terra_30_fscore}  
+\end{figure*}
+
+\begin{figure*}[]
+
+  \centering
+    \includegraphics[scale=0.7]{graphics/sony/halfData/fscore-10-sony}
+    \caption{F-Score, 10\% Training Data, Mobile Phone dataset}
+   \label{fig:sony_10_fscore_half}  
+\end{figure*}
+
+\begin{figure*}[]
+
+  \centering
+    \includegraphics[scale=0.7]{graphics/sony/halfData/fscore-30-sony}
+    \caption{F-Score, 30\% Training Data, Mobile Phone dataset}
+   \label{fig:sony_30_fscore_half}  
+\end{figure*}
+
+\begin{figure*}[]
+
+  \centering
+    \includegraphics[scale=0.7]{graphics/sony/halfData/fscore-60-sony}
+    \caption{F-Score, 60\% Training Data, Mobile Phone dataset}
+   \label{fig:sony_60_fscore_half}  
+\end{figure*}
+
+\begin{figure*}[]
+
+  \centering
+    \includegraphics[scale=0.7]{graphics/sony/halfData/fscore-90-sony}
+    \caption{F-Score, 90\% Training Data, Mobile Phone dataset}
+   \label{fig:sony_90_fscore_half}  
+\end{figure*}
+
+%more data!
+
+\begin{figure*}[]
+
+  \centering
+    \includegraphics[scale=0.7]{graphics/sony/moreData/fscore-10-sony}
+    \caption{F-Score, 10\% Training Data, Mobile Phone dataset, More Features and Data}
+   \label{fig:sony_10_fscore_more}  
+\end{figure*}
+
+\begin{figure*}[]
+
+  \centering
+    \includegraphics[scale=0.7]{graphics/sony/moreData/fscore-30-sony}
+    \caption{F-Score, 30\% Training Data, Mobile Phone dataset,More Features and Data}
+   \label{fig:sony_30_fscore_more}  
+\end{figure*}
+
 \end{document}

### 2012-09-03 docs/paper.tex
Finished conclutions and future work

--- 2012-09-02 docs/paper.tex
@@
 First a semi-supervised method should allow to classify text by annotating only a small portion of data,thus reducing the labor of annotating.\\
-Second the unlabeled data is used during training, this is important since the amount of unlabeled data in these tasks is abundant and available, therefore it can be used to provide extra knowledge to the model.\\
+Second the unlabeled data is used during training, this is important since the amount of unlabelled data in these tasks is abundant and available, therefore it can be used to provide extra knowledge to the model.\\
 \\
@@
 \\
-In respect to short text classification ~\cite{Fan:2010:NMC:1916732.1917677} proposes  to do Feature Extension to deal with data sparcity, in his approach each comment is extended with extra words from an expansion vocabulary.\\
+In respect to short text classification Xinghua and Hongge ~\cite{Fan:2010:NMC:1916732.1917677} proposes  to do Feature Extension to deal with data sparcity, in their approach each comment is extended with extra words from an expansion vocabulary.\\
 ~\cite{Gabrilovich:2006:OBB:1597348.1597395} proposes on the other hand to use encyclopedic knowledge from wikipedia for extending the short comments.\\
@@
 Two semi-supervised techniques are used, Label Propagation ~\cite{Zhu:2005:SLG:1104523}  and  a variation of Structural learning problem for multitasks ~\cite{Ando:2005:FLP:1046920.1194905}.\\
-The next sections describe briefly each of the proposed methods and how they were adapted to the task, then the pre-processing involved. \\
+The next sections describe briefly  the preprocessing of the tweets,each of the proposed semi-supervised methods and how they were adapted to the task. \\
 Addionally the results are shown, where both methods are compared among themselves and to a supervised approach.
@@
 \begin{itemize}
-	\item Sportwear dataset
+	\item Sportswear dataset
 	\item Mobile-Phone dataset
-	\item hygienic-product dataset
+	\item Hygienic-product dataset
 \end{itemize}
@@
 As a result of this pre-processing each comment is converted into a bag of keywords.\\
-This will be later transform into a vector space representation.
-
-%% for future work mention that words like 'camera' that turn out to be good predictor, can be biased by the fact that is misswritten 'camera '  'cmarea'
+This will be later transformed into a vector space representation.
 
@@
 This Semi-supervised learning graph method was proposed by Zhu ~\cite{Zhu:2005:SLG:1104523}.\\
-The idea behind Label propagation is similar to K-Neighbors, nevertheless Label propagation make use of the unlabeled data during the training process.\\
+The idea behind Label propagation is similar to K-Neighbours, nevertheless Label propagation make use of the unlabelled data during the training process.\\
 
@@
 at each step the algorithm will push the labels
-of the labeled data points through the arcs of high weights.The underlying assumption is that instances among a class will have high weighted arcs
+of the labelled data points through the arcs of high weights.The underlying assumption is that instances among a class will have high weighted arcs
 connecting them.\\
@@
 \\
-More sophisticated versions of this approach have been presented and assessed, in ~\cite{Talukdar:2010:EGS:1858681.1858830} Talukdar and Pereira showed an empirical comparison among different variations of the LP algorithm, a modified absortion algorithm is presented where seed labels are not clamped,and it is shown to have better performance in the given tasks.
+More sophisticated versions of this approach have been presented and assessed, in ~\cite{Talukdar:2010:EGS:1858681.1858830} Talukdar and Pereira showed an empirical comparison among different variations of the LP algorithm, a modified absorption algorithm is presented where seed labels are not clamped,and it is shown to have better performance in the given tasks.
 Nevertheless within this paper we call LP to the algorithm proposed by Zhu ~\cite{Zhu:2005:SLG:1104523}.\\
@@
 the underlying assumption is that by solving the auxiliary problems one should be able to find good predictive structures.\\
-The Auxiliary Tasks are trained on the unlabeled data,in consequence one constraint to the creation of auxiliary tasks is that they should be able to automatically generate training data from the target's problem unlabelled data.In ~\cite{Ando:2005:HSL:1219840.1219841} it is argued that having a high number of auxiliary tasks is beneficial for the performance.\\
+The Auxiliary Tasks are trained on the unlabelled data,in consequence one constraint to the creation of auxiliary tasks is that they should be able to automatically generate training data from the target's problem unlabelled data.In ~\cite{Ando:2005:HSL:1219840.1219841} it is argued that having a high number of auxiliary tasks is beneficial for the performance.\\
 \\
@@
 The auxiliary problems are defined as:\\
-Learn a linear predictor using the Unlabelled data for the $K$ most common words in the unlabeled data and a predictor for the words with highest Pointwise mutual information(PMI) from the Labelled Data.\\
+Learn a linear predictor using the Unlabelled data for the $K$ most common words in the unlabelled data and a predictor for the words with highest Pointwise mutual information(PMI) from the Labelled Data.\\
+By doing this both the features of the labelled data and unlabelled data will be extended, the labelled data will be extended with features from the unlabelled data, and the unlabelled data will be extended with predictive features of the labelled data.\\
 \\
@@
 Subsequently a linear classifier for predicting each of this words is trained using the unlabelled data.
-It is clear that labels for this tasks can be easily generated by masking the words for which the classifiers are being trained from the comments.\\
+It is clear that labels for this tasks can be easily generated by masking the words for which the classifiers are being trained to predict.\\
 \\
-By solving the auxiliary tasks, the feauture vectors of the training data for the target problem can be extended with the predictions of the auxiliary tasks.\\
-This might shown useful in the setup of the experiment, since we are extending the feauture representations from knowledge of unlabelled data.\\
+By solving the auxiliary tasks, the feature vectors of the training data for the target problem can be extended with the predictions of the auxiliary tasks.\\
+This might shown useful in the setup of the experiment, since we are extending the feature representations from knowledge of unlabelled data.\\
 \\
 Finally a linear classifier is learnt using the training data for the target problem.\\
-With respect to the ASO-SVD algorithm, this paper just explore a naive approach by using auxiliary problems, in this regard the auxiliary classifiers are used to extend the feature vectors.
-
-\section{Feature Generation}
+With respect to the ASO-SVD algorithm, this paper just explore a naive approach by using auxiliary problems, in this regard the auxiliary classifiers are used to extend the feature vectors.\\
+For the rest of the paper we will refer to this approach as Naive SL.
 
@@
 For the Label Propagation  $Junto$ \footnote{ \url{https://github.com/parthatalukdar/junto} } ~\cite{Talukdar:2010:EGS:1858681.1858830} was used.
-$Junto$ is an open source implementation of the Label Propagation algorithm proposed by Zhu.\\
+$Junto$ is an open source implementation of the Label Propagation algorithm.\\
 \\
 For $SL$ and $SVM$ the libsvm\footnote{\url{http://www.csie.ntu.edu.tw/~cjlin/libsvm/}} library provided an implementation for training SVM.\\
-For all the linear classifiers trained in the experiments a  polynomial Kernel was picked and the value of $gamma$ was 1.2, the reason behind this choice is motivated by the empirical results obtained by ~\cite{Joachims:1998:TCS:645326.649721} in a similar task.
+For all the linear classifiers trained in the experiments a  polynomial Kernel was picked and the value of $gamma$ was 1.2, the reason behind this choice is motivated by the empirical results obtained by ~\cite{Joachims:1998:TCS:645326.649721} in a similar task.\\
+\\
+For making the tasks suitable for the given computational power, a subset of the size of $\frac{1}{4}$ of each of the given datasets was used, this has a major drawback, since the more the data the better the behaviour of the semi-supervised algorithms.
+Furthermore an upper bound on the number of auxiliary classifiers created by  the naive structure learning was imposed, the auxiliary problems would be 40\% of the most common words in the unlabelled data and the words with highest PMI from the Labelled data.\\
+A major drawback of Label Propagation from a running time perspective is having to calculate a complete graph containing the similarity among the nodes.Calculating a graph with 2 or more millions of arcs consume lots of resources.
+\section{Results}
+In overall the Naive SL could maintain the f-score given by the Supervised approach, in some cases was able to get a much better f-score by improving recall, in some other cases a slightly better recall resulted in a decline of the precision thus leading to a worse f-score.\\
+\\
+The LP approach on the other hand raised in labels where both of the previous approaches failed such as with the label $Resistance$  in the sportswear dataset Figure~\ref{fig:nike_90_fscore} or $Brand$ $Support$ Figure~\ref{fig:nike_10_fscore},  $Tenderness$  in the Hygienic Product dataset Figure~\ref{fig:terra_30_fscore}, and many others like $Photography$,$Screen$ and $Social$ $Networks$ in the Mobilephone dataset Figure~\ref{fig:sony_30_fscore_more}.\\
+\\
+The Hygienic Product and Sportswear datasets shown some decent results, whereas the Mobile Phone dataset shown to be challenging.\\
+\\
+One factor that might have affected the overall performance was using a subset of the data, this specially seems to affect LP.\\
+LP profits from abundant unannotated data, my hypothesis is that using a very small set of seeds with a large number of unannotated data should improve the scores given below.\\
+The reason for LP giving such low scores  on some of the tasks might be caused by the limitation on the dataset sizes and the data sparsity in the feature vectors.\\
+\\
+First the Limitation on the size of the datasets might have caused a lack of extra samples, thus  generating some disconnected segments of the graph in case of LP, therefore a proper propagation cannot be carried out successfully for prediction.\\
+\\
+Second the feature vectors are very sparse, because of the bag of keywords approach and the short text nature of the task, thus leading also to disconnected segments of the graph.\\
+\\
+A second test was carried out in an attempt to discover whether both more data and selecting more features would benefit the approach, this second test was done on the Mobile Phone dataset.\\
+In this trial more data were taken into account and a larger number of features were allowed to be part of the feature vectors,this would also benefit SL since the number of auxiliary problems would be incremented.
+The results are given in Figure~\ref{fig:sony_10_fscore_more} and Figure~\ref{fig:sony_30_fscore_more}, in general it can be said that there is much a better f-score for a larger number of labels when compared to the previous tests, so It is possible to speculate that using the whole datasets would greatly increase the f-scores given in this report.\\
+\\
 
-La
+Since comments are reduced to a bag of keywords other factors which could have caused the given results are:
+\begin{itemize}
+\item \textbf{Noise}:the given data is actual user-generated content thus very noisy.\\
+Noisy data such as miss written words can lead to bad classifications or points isolated in the LP graph.
+Take as an example the label $Camera$ for the Mobile phone dataset, if a good predictor for this label is the actual word ''camera" and this word has been seen in the labelled data, seeing variations such as ''camraa" might not result predictive, since they would be in a different dimension.
 
-\section{Results}
+\item \textbf{Sparsity and Short Text}: feature vectors are very sparse and text is short.
+This could affect in the following ways, lets think again on the label $Camera$ for the Mobile  phone dataset, if we assume we are classifying long texts, an annotated instance can reveal a lot of the topic vocabulary , in this case words such as ''resolution", ''megapixels" and so on.\\
+On the other hand in the short text classification, you got at most 144 characters per text, so you might end up only with a small subset of topic related words.
+For example lets assume you have a set of good predictors in your labelled data and those predictors are the words: ''Camera" and ''resolution".If there is a comment saying just: ''it has a good amount of megapixels", it will be very unlikely to be classified correctly, unless there is another comment linking ''megapixels" with one of the predicting words in the seed set.\\
+\\
+With respect to the Topic Vocabulary, I would speculate that this really affect the performance.
+In the Hygienic Product and  Sportswear the term's range are more or less reduced, this is not the case of the mobile phone dataset, the range of topic vocabulary for each label is huge, just take into account the label $Application$, a comment can be given this label if it has a mention to a well known IOS or Android App, such as ''Angry Birds", furthermore take into account the label $Social$ $Network$ where social networks' names are mentioned.
+On top of that combine all the possible technical words that might appear with the labels $Camera$, $OS$, $Photography$.
 
-\section{Future Work}
+\end{itemize}
+
+\section{Conclusions and Future Work}
+An experiment on classifying short comments about products was described, two semi-supervised approaches were presented and compared for solving this problem.\\
+\\
+Data sparsity and the length of the texts shown to be an issue in this task for Label Propagation.
+One idea for tackling this problem would be to try injecting some knowledge related to the labels, this could be useful in the difficult tasks such as the Mobile Phone dataset.An approach similar to the one given by ~\cite{Gabrilovich:2006:OBB:1597348.1597395} could be tried.Basically Wikipedia could be used to gather Topic vocabulary and use that vocabulary to extend each of the comments, this could solve disconnected segments in the graph.\\
+\\
+Another idea worth trying is to use the SL for multitask classification instead of tackling each dataset by separate, one could try joining them and solving them as a single classification problem, this however requires more computational power but should allow better results.\\
+\\
+In spite of noise being a problem, I would speculate that given enough data the problem of noisy entries such as miss-spelled words should not be a big issue, this assuming there is enough noisy data in both the labelled and unlabelled entries.\\
+\\
+It would be also interesting to try the other Label Propagation Variations such as Modified Adsorption (MAD) discussed in ~\cite{Talukdar:2010:EGS:1858681.1858830}, these implementations are available in Junto.\\
+MAD should help when dealing with noisy input labels, which was one of the case between $Photography$ and $Camera$ in the Mobile Phone dataset.\\
+\\
+Additionally considering joining the naive SL given here with LP should help the latter to get better scores, this by allowing to connect some of the isolated sub-graphs generated by the feature sparsity.
+
 %other LP variations ( MAD for noisy ..)

### 2012-09-03 docs/paper.tex
Abstract added, format modified

@@
     \maketitle
-   \begin{abstract}
-      ...
-    \end{abstract}
   \end{@twocolumnfalse}
  ]
+
+   \begin{abstract}
+      Microblogging has become a trend,thus many users are using such platforms to share their opinions.Mining these opinions can reveal valuable information to companies, such as what features to develop in their products or marketing strategies.However there are  major drawbacks when mining tweets, first their length do not provide enough word occurrences so traditional bag-of-words methods have limitations, second they are extremely noisy,and third annotated data is limited and costly to get.\\
+      In this paper we address the problem of classifying short product reviews by using semisupervised learning.
+A Comparison among two semisupervised methods and a supervised method is given.
+Finally we propose different ways to improve the given results by injecting knowledge into the semisupervised models.
+    \end{abstract}
 
@@
 \\
-In ~\cite{Ando:2005:FLP:1046920.1194905} Zhang and Kubota proposed a semi-supervised approach using linear classifiers for multiple learning tasks.\\
+Zhang and Kubota ~\cite{Ando:2005:FLP:1046920.1194905} proposed a semi-supervised approach using linear classifiers for multiple learning tasks.\\
 They proposed to create additional classifications tasks (Auxiliary Problems) aside from the Target Problem.\\
@@
 \\
-Though Classifying text has been a widely studied topic,the focus has been on long documents,
+Even though Classifying text has been a widely studied topic,the focus has been on long documents,
 whereas tweets are at most 144 characters long.\\
@@
 The auxiliary problems are defined as:\\
-Learn a linear predictor using the Unlabelled data for the $K$ most common words in the unlabelled data and a predictor for the words with highest Pointwise mutual information(PMI) from the Labelled Data.\\
+Learning a linear predictor using the Unlabelled data for the $K$ most common words in the unlabelled data and a predictor for the words with highest Pointwise mutual information(PMI) from the Labelled Data.\\
 By doing this both the features of the labelled data and unlabelled data will be extended, the labelled data will be extended with features from the unlabelled data, and the unlabelled data will be extended with predictive features of the labelled data.\\

### 2012-09-03 docs/paper.tex
fixed capitalizations

@@
       In this paper we address the problem of classifying short product reviews by using semisupervised learning.
-A Comparison among two semisupervised methods and a supervised method is given.
+A comparison among two semisupervised methods and a supervised method is given.
 Finally we propose different ways to improve the given results by injecting knowledge into the semisupervised models.
@@
 Twitter and Tuenti are popular microblogging services in Latinamerica,
-as prices of Smartphones became more accessible to people big communities
+as prices of smartphones became more accessible to people big communities
 have grown around this services.\\
@@
 \\
-In the Scenario of text classification Semi-supervised techniques present two advantages:\\
+In the scenario of text classification Semi-supervised techniques present two advantages:\\
 First a semi-supervised method should allow to classify text by annotating only a small portion of data,thus reducing the labor of annotating.\\
@@
 \\
-Even though Classifying text has been a widely studied topic,the focus has been on long documents,
+Even though classifying text has been a widely studied topic,the focus has been on long documents,
 whereas tweets are at most 144 characters long.\\
@@
 This approach maps the data to a graph representation.
-In this representation each Arc of the graph will connect two nodes only if the two nodes are similar,
+In this representation each arc of the graph will connect two nodes only if the two nodes are similar,
 the weights of the arcs are directly proportional to the similarity of the incident nodes.\\
@@
 \\
-\textbf{Step 1 - Init}: In this step, the Labels for $Y_{L}$ are clamped, and the labels for $Y_{U}$ are randomly initialized.\\
+\textbf{Step 1 - Init}: In this step, the labels for $Y_{L}$ are clamped, and the labels for $Y_{U}$ are randomly initialized.\\
 The proof that the initialization values of $Y_{U}$ are not transcendental can be found at ~\cite{Zhu:2005:SLG:1104523}.\\
 \\
-\textbf{Step 2 - Propagation}: In this step, the Labels of neighbouring nodes are pushed.\\
+\textbf{Step 2 - Propagation}: In this step, the labels of neighbouring nodes are pushed.\\
 Let $t$ be the current iteration, then $Y^{t+1}$ is defined as:
@@
 The auxiliary problems are defined as:\\
-Learning a linear predictor using the Unlabelled data for the $K$ most common words in the unlabelled data and a predictor for the words with highest Pointwise mutual information(PMI) from the Labelled Data.\\
+learning a linear predictor using the Unlabelled data for the $K$ most common words in the unlabelled data and a predictor for the words with highest Pointwise mutual information(PMI) from the labelled Data.\\
 By doing this both the features of the labelled data and unlabelled data will be extended, the labelled data will be extended with features from the unlabelled data, and the unlabelled data will be extended with predictive features of the labelled data.\\
 \\
-For learning this tasks, first the Words with highest PMI are found using the labelled data, then the words with highest frequency in the unlabelled data are found.\\
+For learning this tasks, first the words with highest PMI are found using the labelled data, then the words with highest frequency in the unlabelled data are found.\\
 Subsequently a linear classifier for predicting each of this words is trained using the unlabelled data.
@@
 For $SL$ and $SVM$ the libsvm\footnote{\url{http://www.csie.ntu.edu.tw/~cjlin/libsvm/}} library provided an implementation for training SVM.\\
-For all the linear classifiers trained in the experiments a  polynomial Kernel was picked and the value of $gamma$ was 1.2, the reason behind this choice is motivated by the empirical results obtained by ~\cite{Joachims:1998:TCS:645326.649721} in a similar task.\\
+For all the linear classifiers trained in the experiments a  Polynomial Kernel was picked and the value of $gamma$ was 1.2, the reason behind this choice is motivated by the empirical results obtained by ~\cite{Joachims:1998:TCS:645326.649721} in a similar task.\\
 \\
@@
 \section{Results}
-In overall the Naive SL could maintain the f-score given by the Supervised approach, in some cases was able to get a much better f-score by improving recall, in some other cases a slightly better recall resulted in a decline of the precision thus leading to a worse f-score.\\
+In overall the Naive SL could maintain the f-score given by the supervised approach, in some cases was able to get a much better f-score by improving recall, in some other cases a slightly better recall resulted in a decline of the precision thus leading to a worse f-score.\\
 \\
@@
 \\
-With respect to the Topic Vocabulary, I would speculate that this really affect the performance.
+With respect to the topic vocabulary, I would speculate that this really affect the performance.
 In the Hygienic Product and  Sportswear the term's range are more or less reduced, this is not the case of the mobile phone dataset, the range of topic vocabulary for each label is huge, just take into account the label $Application$, a comment can be given this label if it has a mention to a well known IOS or Android App, such as ''Angry Birds", furthermore take into account the label $Social$ $Network$ where social networks' names are mentioned.

### 2012-09-03 docs/paper.tex
fixed capitalization,punctuation and format

@@
 
-\author{David Przybilla\\dav.alejandro@gmail.com, davida@coli.uni-saarland.de\\ \\ Term Paper for Unsupervised Semi-supervised
+\author{David Przybilla\\dav.alejandro@gmail.com, davida@coli.uni-saarland.de\\ \\ Term Paper for Unsupervised semisupervised
 Learning Seminar\\ Universit\"{a}t des Saarlandes}
-\title{Classification of short product Reviews using Semi-Supervised Learning}
+\title{Classification of short product reviews using semisupervised learning}
 \begin{document}
@@
    \begin{abstract}
-      Microblogging has become a trend,thus many users are using such platforms to share their opinions.Mining these opinions can reveal valuable information to companies, such as what features to develop in their products or marketing strategies.However there are  major drawbacks when mining tweets, first their length do not provide enough word occurrences so traditional bag-of-words methods have limitations, second they are extremely noisy,and third annotated data is limited and costly to get.\\
+      Microblogging has become a trend,thus many users are using such platforms to share their opinions.Mining these opinions can reveal valuable information to companies, such as what features to develop in their products or marketing strategies.However there are  major drawbacks when mining tweets, first their length do not provide enough word occurrences so traditional bag-of-words methods have limitations, second they are extremely noisy and third annotated data is limited and costly to get.\\
       In this paper we address the problem of classifying short product reviews by using semisupervised learning.
@@
 \\
-One of the subtasks of Sentiment Analysis is to find the Topic or Aspect of an opinion,
+One of the subtasks of Sentiment Analysis is to find the topic or aspect of an opinion,
 for example given a set of opinions about a mobile phone, it is possible to label each comment
@@
 \\
-In the scenario of text classification Semi-supervised techniques present two advantages:\\
-First a semi-supervised method should allow to classify text by annotating only a small portion of data,thus reducing the labor of annotating.\\
-Second the unlabeled data is used during training, this is important since the amount of unlabelled data in these tasks is abundant and available, therefore it can be used to provide extra knowledge to the model.\\
+In the scenario of text classification semisupervised techniques present two advantages:\\
+First a semisupervised method should allow to classify text by annotating only a small portion of data,thus reducing the labor of annotating.\\
+Second the unlabelled data is used during training, this is important since the amount of unlabelled data in these tasks is abundant and available, therefore it can be used to provide extra knowledge to the model.\\
 \\
-Zhang and Kubota ~\cite{Ando:2005:FLP:1046920.1194905} proposed a semi-supervised approach using linear classifiers for multiple learning tasks.\\
+Zhang and Kubota ~\cite{Ando:2005:FLP:1046920.1194905} proposed a semisupervised approach using linear classifiers for multiple learning tasks.\\
 They proposed to create additional classifications tasks (Auxiliary Problems) aside from the Target Problem.\\
 The underlying idea is that the auxiliary problems will help finding good predictive structures.\\
-One of the constraints in this approach is that auxiliary problems should be  able to automatically generate labelled data from the original unlabeled data.
+One of the constraints in this approach is that auxiliary problems should be  able to automatically generate labelled data from the original unlabelled data.
 This method has been used in tasks such as Text Chunking ~\cite{Ando:2005:HSL:1219840.1219841}\\
@@
 In contrast ~\cite{Zhu:2005:SLG:1104523} proposes a graph approach called label propagation for
-doing semi-supervised learning.\\
+doing semisupervised learning.\\
 This approach maps the data to a graph representation, then labelled instances propagate their labels through the graph, allowing unlabelled data to adopt the label of those instances which are similar.\\
@@
 This paper describes the setup of an experiment for classifying short-text comments of product reviews extracted from twitter.\\
-Two semi-supervised techniques are used, Label Propagation ~\cite{Zhu:2005:SLG:1104523}  and  a variation of Structural learning problem for multitasks ~\cite{Ando:2005:FLP:1046920.1194905}.\\
-The next sections describe briefly  the preprocessing of the tweets,each of the proposed semi-supervised methods and how they were adapted to the task. \\
+Two semisupervised techniques are used, Label Propagation ~\cite{Zhu:2005:SLG:1104523}  and  a variation of Structural learning problem for multitasks ~\cite{Ando:2005:FLP:1046920.1194905}.\\
+The next sections describe briefly  the preprocessing of the tweets,each of the proposed semisupervised methods and how they were adapted to the task. \\
 Addionally the results are shown, where both methods are compared among themselves and to a supervised approach.
@@
 The Datasets of this experiments were provided by Meridean.\\
-Meridean\footnote{\url{http://http://merideangroup.com/}} is a Colombian company which extracts tweets
+Meridean\footnote{\url{http://merideangroup.com/}} is a Colombian company which extracts tweets
 mentioning latinamerican companies or products.\\
@@
 
-When it comes to pre-processing there could be wide number of possible 
+When it comes to pre-processing there could be a wide number of possible 
 tasks that can be done, I try to keep it simple given the time constraints. \\
@@
 
-This Semi-supervised learning graph method was proposed by Zhu ~\cite{Zhu:2005:SLG:1104523}.\\
-The idea behind Label propagation is similar to K-Neighbours, nevertheless Label propagation make use of the unlabelled data during the training process.\\
+This semisupervised learning graph method was proposed by Zhu ~\cite{Zhu:2005:SLG:1104523}.\\
+The idea behind Label propagation is similar to K-Neighbours, nevertheless Label Propagation make use of the unlabelled data during the training process.\\
 
@@
 \\
-Given our semi-supervised task, then $Y$ can be divided into:\\
+Given our semisupervised task, then $Y$ can be divided into:\\
 \\
@@
 \\
-To summarize, in the experiment we convert our data into a complete graph,
+To summarize in our experiment we convert our data into a complete graph,
 each node is the feature vector of a comment, and the weight of each arc
@@
 \section{Structure Learning}
-A Semi-supervised learning method proposed in ~\cite{Ando:2005:FLP:1046920.1194905}.\\
+A semisupervised learning method proposed in ~\cite{Ando:2005:FLP:1046920.1194905}.\\
 This paper proposes a way to learn multiple classification tasks.In this approach the original Classification Task(Target Problem) is extended by creating a set of auxiliary classification tasks.\\
-The Auxiliary Classification tasks are used to improve performance on the target task,
+The auxiliary classification tasks are used to improve performance on the target task,
 the underlying assumption is that by solving the auxiliary problems one should be able to find good predictive structures.\\
@@
 \\
-In this paper's experiment, the target task corresponds to find the label of each comment.\\
+In this paper's experiment, the target task corresponds to find the topic of each comment.\\
 The auxiliary problems are defined as:\\
 learning a linear predictor using the Unlabelled data for the $K$ most common words in the unlabelled data and a predictor for the words with highest Pointwise mutual information(PMI) from the labelled Data.\\
-By doing this both the features of the labelled data and unlabelled data will be extended, the labelled data will be extended with features from the unlabelled data, and the unlabelled data will be extended with predictive features of the labelled data.\\
+By doing this, both the features of the labelled data and unlabelled data will be extended, the labelled data will be extended with features from the unlabelled data, and the unlabelled data will be extended with predictive features of the labelled data.\\
 \\
 For learning this tasks, first the words with highest PMI are found using the labelled data, then the words with highest frequency in the unlabelled data are found.\\
-Subsequently a linear classifier for predicting each of this words is trained using the unlabelled data.
+Subsequently a linear classifier for predicting each of the most common words is trained using the unlabelled data, and a linear classifier for predicting each of the most predictive words is trained using the labelled data.
 It is clear that labels for this tasks can be easily generated by masking the words for which the classifiers are being trained to predict.\\
 \\
-By solving the auxiliary tasks, the feature vectors of the training data for the target problem can be extended with the predictions of the auxiliary tasks.\\
+By solving the auxiliary tasks, the feature vectors of the training data for the target problem can be extended with the predictions of the auxiliary tasks.Also the vectors of the unlabelled data are extended.\\
 This might shown useful in the setup of the experiment, since we are extending the feature representations from knowledge of unlabelled data.\\
@@
 	\item Single task Supervised Learning using SVM ($SVM$)
-	\item Single task Semi-supervised Learning using Label Propagation ($LP$)
-	\item Single task Semi-supervised Learning using The naive Structural Learning($SL$)
+	\item Single task semisupervised Learning using Label Propagation ($LP$)
+	\item Single task semisupervised Learning using The naive Structural Learning($SL$)
 
@@
 \\
-For making the tasks suitable for the given computational power, a subset of the size of $\frac{1}{4}$ of each of the given datasets was used, this has a major drawback, since the more the data the better the behaviour of the semi-supervised algorithms.
+For making the tasks suitable for the given computational power, a subset of the size of $\frac{1}{4}$ of each of the given datasets was used, this has a major drawback, since the more the data the better the behaviour of the semisupervised algorithms.
 Furthermore an upper bound on the number of auxiliary classifiers created by  the naive structure learning was imposed, the auxiliary problems would be 40\% of the most common words in the unlabelled data and the words with highest PMI from the Labelled data.\\
@@
 \\
-First the Limitation on the size of the datasets might have caused a lack of extra samples, thus  generating some disconnected segments of the graph in case of LP, therefore a proper propagation cannot be carried out successfully for prediction.\\
+First the Limitation on the size of the datasets might have caused a lack of extra samples, thus  generating some disconnected segments of the graph in case of LP, therefore a proper propagation could not be carried out successfully for prediction.\\
 \\
@@
 Noisy data such as miss written words can lead to bad classifications or points isolated in the LP graph.
-Take as an example the label $Camera$ for the Mobile phone dataset, if a good predictor for this label is the actual word ''camera" and this word has been seen in the labelled data, seeing variations such as ''camraa" might not result predictive, since they would be in a different dimension.
+Take as an example the label $Camera$ for the Mobile phone dataset, if a good predictor for this label is the actual word ``camera" and this word has been seen in the labelled data, seeing variations such as ``camraa" might not result predictive, since they would be in a different dimension.
 
 \item \textbf{Sparsity and Short Text}: feature vectors are very sparse and text is short.
-This could affect in the following ways, lets think again on the label $Camera$ for the Mobile  phone dataset, if we assume we are classifying long texts, an annotated instance can reveal a lot of the topic vocabulary , in this case words such as ''resolution", ''megapixels" and so on.\\
+This could affect in the following ways, lets think again on the label $Camera$ for the Mobile  phone dataset, if we assume we are classifying long texts, an annotated instance can reveal a lot of the topic vocabulary , in this case words such as ``resolution", ``megapixels" and so on.\\
 On the other hand in the short text classification, you got at most 144 characters per text, so you might end up only with a small subset of topic related words.
-For example lets assume you have a set of good predictors in your labelled data and those predictors are the words: ''Camera" and ''resolution".If there is a comment saying just: ''it has a good amount of megapixels", it will be very unlikely to be classified correctly, unless there is another comment linking ''megapixels" with one of the predicting words in the seed set.\\
+For example lets assume you have a set of good predictors in your labelled data and those predictors are the words: ``Camera" and ``resolution".If there is a comment saying just: ``it has a good amount of megapixels", it will be very unlikely to be classified correctly, unless there is another comment linking ``megapixels" with one of the predicting words in the seed set.\\
 \\
 With respect to the topic vocabulary, I would speculate that this really affect the performance.
-In the Hygienic Product and  Sportswear the term's range are more or less reduced, this is not the case of the mobile phone dataset, the range of topic vocabulary for each label is huge, just take into account the label $Application$, a comment can be given this label if it has a mention to a well known IOS or Android App, such as ''Angry Birds", furthermore take into account the label $Social$ $Network$ where social networks' names are mentioned.
+In the Hygienic Product and  Sportswear the term's range are more or less reduced, this is not the case of the mobile phone dataset, the range of topic vocabulary for each label is huge, just take into account the label $Application$, a comment can be given this label if it has a mention to a well known IOS or Android App, such as ``Angry Birds", furthermore take into account the label $Social$ $Network$ where social networks' names are mentioned.
 On top of that combine all the possible technical words that might appear with the labels $Camera$, $OS$, $Photography$.
@@
 \section{Conclusions and Future Work}
-An experiment on classifying short comments about products was described, two semi-supervised approaches were presented and compared for solving this problem.\\
+An experiment on classifying short comments about products was described, two semisupervised approaches were presented and compared for solving this problem.\\
 \\
-Data sparsity and the length of the texts shown to be an issue in this task for Label Propagation.
+Data sparsity and the length of the texts shown to be an issue for Label Propagation.
 One idea for tackling this problem would be to try injecting some knowledge related to the labels, this could be useful in the difficult tasks such as the Mobile Phone dataset.An approach similar to the one given by ~\cite{Gabrilovich:2006:OBB:1597348.1597395} could be tried.Basically Wikipedia could be used to gather Topic vocabulary and use that vocabulary to extend each of the comments, this could solve disconnected segments in the graph.\\
 \\
-Another idea worth trying is to use the SL for multitask classification instead of tackling each dataset by separate, one could try joining them and solving them as a single classification problem, this however requires more computational power but should allow better results.\\
+Another idea worth trying is to use the SL for multitask classification instead of tackling each dataset by separate, it might be beneficial  to  join them and solve them as a single classification problem.However this requires more computational power but  at the same time it should allow better results.\\
 \\
@@
 \\
-It would be also interesting to try the other Label Propagation Variations such as Modified Adsorption (MAD) discussed in ~\cite{Talukdar:2010:EGS:1858681.1858830}, these implementations are available in Junto.\\
-MAD should help when dealing with noisy input labels, which was one of the case between $Photography$ and $Camera$ in the Mobile Phone dataset.\\
+It would be also interesting to try the other Label Propagation variations such as Modified Adsorption (MAD) discussed in ~\cite{Talukdar:2010:EGS:1858681.1858830}, these implementations are available in Junto.\\
+MAD should help when dealing with noisy input labels, which was one of the cases between $Photography$ and $Camera$ in the Mobile Phone dataset.\\
 \\
-Additionally considering joining the naive SL given here with LP should help the latter to get better scores, this by allowing to connect some of the isolated sub-graphs generated by the feature sparsity.
+Finally considering joining the naive SL given here with LP should help the latter to get better scores, this by allowing to connect some of the isolated sub-graphs generated by the feature sparsity.
 
